---
title: "Single_Cells_HR"
author: "Chaoting Zhou"
date: "7/10/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::knit_hooks$set(optipng = knitr::hook_optipng)
```

```{r}
setwd("/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/data_analysis")
```



```{r}
library(Seurat)
library(tidyverse)
library(Matrix)
library(scales)
library(cowplot)
library(RCurl)
library(DropletUtils)
```

```{r}
 data_dirs <- c("/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0428/032323")
 # Read the RNA and HTO data
  counts <- Read10X(data_dirs)
  hto_seurat <- as.data.frame(counts$`Hashtag`)
  rownames( hto_seurat)
  hto_seurat <- hto_seurat[-c(1:5),]
  rownames( hto_seurat)

  # Create the Seurat objects
  rna_seurat <- CreateSeuratObject(counts = counts$`Gene Expression`, project = "RNA",min.cells = 3,    min.features = 200)
  adt_seurat <- CreateSeuratObject(counts = counts$`Antibody Capture`, project = "ADT")

  # Determine common cell barcodes
common_cells <- Reduce("intersect",x=list(colnames(rna_seurat),colnames(adt_seurat)))
  length(common_cells)
  rna_seurat <- rna_seurat[,common_cells]
  adt_seurat <- adt_seurat[,common_cells]
  hto_seurat <- hto_seurat[,common_cells]
  # Subset Seurat objects and HTO data to common cell barcaroles
  rna_seurat[["HTO"]] <- CreateAssayObject(counts = hto_seurat)
  adt_seurat[["HTO"]] <- CreateAssayObject(counts = hto_seurat)
  head(rna_seurat)
  
  rna_seurat <- NormalizeData(rna_seurat)
  rna_seurat <- FindVariableFeatures(rna_seurat, selection.method = "vst")
  rna_seurat <- ScaleData(rna_seurat, features = VariableFeatures(rna_seurat)) 

  rna_seurat_1 <- NormalizeData(rna_seurat, 
                             assay = "HTO", 
                             normalization.method = "CLR")

  rna_seurat_1 <- HTODemux(rna_seurat_1,
                        assay = "HTO", 
                        positive.quantile = 0.99)

  table(rna_seurat$nFeature_HTO)
  sample <- table(rna_seurat$hash.ID)




```{r cars}
summary(cars)
```

```{r}
data0323.dir <- "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0428/032323"
rna_counts <- Read10X(data0323.dir)
rna_seurat <- CreateSeuratObject(counts = rna_counts$`Gene Expression`, project = "RNA",min.cells = 3, min.features = 200)
head(rna_seurat)
rna_seurat <- FindVariableFeatures(rna_seurat, selection.method = "vst")
all.genes <- rownames(rna_seurat)
rna_seurat <- ScaleData(rna_seurat, features = all.genes)
rna_seurat

```


```{r}
hot_counts <- Read10X(data0323.dir)
pbmc.htos <- as.data.frame(hot_counts$`Hashtag`)
rownames(pbmc.htos)
pbmc.htos <- pbmc.htos[-c(1:5),]
rownames(pbmc.htos)
commonDrops <- Reduce("intersect",x=list(colnames(rna_seurat),colnames(pbmc.htos),colnames(adt_seurat)))
length(commonDrops)
rna_seurat <- CreateSeuratObject(counts = rna_counts$`Gene Expression`, project = "RNA",min.cells = 3, min.features = 200)
rna_seurat[["HTO"]] <- CreateAssayObject(counts = pbmc.htos[,commonDrops])
rna_seurat
head(rna_seurat)
```
```{r}
pbmc.hashtag <- NormalizeData(rna_seurat)
#寻找高可变
pbmc.hashtag <- FindVariableFeatures(pbmc.hashtag, selection.method = "mean.var.plot")
#标准化
pbmc.hashtag <- ScaleData(pbmc.hashtag, features = VariableFeatures(pbmc.hashtag))
pbmc.hashtag
```

```{r}
pbmc.htos <- pbmc.htos[,commonDrops]
pbmc.hashtag[["HTO"]] <- CreateAssayObject(counts = pbmc.htos)
pbmc.hashtag
```

```{r}
pbmc.hashtag <- NormalizeData(pbmc.hashtag, 
                             assay = "HTO", 
                             normalization.method = "CLR")
```

```{r}
pbmc.hashtag <- HTODemux(pbmc.hashtag,
                        assay = "HTO", 
                        positive.quantile = 0.99)
```


```{r}
table(pbmc.hashtag$HTO_classification.global)
```

```{r}
pbmc.hashtag@assays
```

```{r}
table(pbmc.hashtag$hash.ID)
```

```{r}
pbmc_hashtag <- Idents(pbmc.hashtag,id = "hash_maxID")
pbmc_hashtag <-Idents(pbmc.hashtag,id = "hash_maxID")
RidgePlot(pbmc.hashtag,features.plot = rownames(GetAssayData(pbmc.hashtag,assay.type = "HTO"))[1:2],nCol = 2)
```
```{r}
P1 <- RidgePlot(object = pbmc.hashtag, features = rownames(GetAssayData(pbmc.hashtag, assay = "HTO"))[1:5])

ggsave(filename = "gene expression0323.png", plot = P1, width = 20, height = 15,dpi = 300)

P1
```

```{r}
Idents(pbmc.hashtag) <- "HTO_classification.global"
p2 <- VlnPlot(pbmc.hashtag, features = "nCount_RNA", pt.size = 0.1, log = TRUE)
ggsave(filename = "gene expression0323_single.png", plot = p2,dpi = 300)
p2
```

```{r, results = 'hold',collapse=TRUE}
hot_counts <- Read10X(data0323.dir)
pbmc.htos <- as.data.frame(hot_counts$`Hashtag`)
rownames(pbmc.htos)
pbmc.htos <- pbmc.htos[-c(1:5),]
rownames(pbmc.htos)
commonDrops <- Reduce("intersect",x=list(colnames(rna_seurat),colnames(pbmc.htos),colnames(adt_seurat)))
length(commonDrops)
Adt_seurat <- CreateSeuratObject(counts = rna_counts$`Antibody Capture`, project = "Anti")
Adt_seurat <- Adt_seurat[,commonDrops]
Adt_seurat[["HTO"]] <- CreateAssayObject(counts = pbmc.htos[,commonDrops])
Adt_seurat
head(Adt_seurat)
```

```{r,collapse = TRUE}
pbmc.htos <- pbmc.htos[,commonDrops]
Adt_seurat[["HTO"]] <- CreateAssayObject(counts = pbmc.htos)
Adt_seurat
head(Adt_seurat)
```

```{r,collapse = TRUE}
Adt_seurat <- NormalizeData(Adt_seurat, 
                             assay = "HTO", 
                             normalization.method = "CLR")

```

```{r}
Adt_seurat <- HTODemux(Adt_seurat,
                        assay = "HTO", 
                        positive.quantile = 0.99)
```

```{r}
table(Adt_seurat$HTO_classification.global)
```



```{r}
data0323.dir <- "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0428/032323"
hot_counts <- Read10X(data0323.dir)
pbmc.htos <- as.data.frame(hot_counts$`Hashtag`)
rownames(pbmc.htos)
pbmc.htos <- pbmc.htos[-c(1:5),]
rownames(pbmc.htos)
HTO_seurat <- CreateSeuratObject(counts = pbmc.htos,project = "HTO")
Adt_seurat <- CreateSeuratObject(counts = hot_counts$`Antibody Capture`, project = "Anti")
rna_seurat <- CreateSeuratObject(counts = hot_counts$`Gene Expression`, project = "RNA",min.cells = 3, min.features = 200)
commonDrops <- Reduce("intersect",x=list(colnames(rna_seurat),colnames(HTO_seurat),colnames(Adt_seurat)))
length(commonDrops)
Adt_seurat 
head(Adt_seurat)
Adt_seurat <- Adt_seurat[,commonDrops]
HTO_seurat <- HTO_seurat[,commonDrops]
rna_seurat <- rna_seurat[,commonDrops]
HTO_seurat[["ADT"]] <- CreateAssayObject(counts = GetAssayData(Adt_seurat, slot = "counts"))
HTO_seurat[["RNA"]] <- CreateAssayObject(counts = GetAssayData(rna_seurat, slot = "counts"))
HTO_seurat
head(HTO_seurat)
HTO_seurat[["ADT"]] <- CreateAssayObject(counts = Adt_seurat[,commonDrops])
HTO_seurat[["RNA"]] <- CreateAssayObject(counts=rna_seurat[,commonDrops])


```
```{r}
data0323.dir <- "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0428/032323"
counts <- Read10X(data0323.dir)
hto <- as.data.frame(counts$`Hashtag`)
rownames(hto)
hto <- hto[-c(1:5),]
rownames(hto)
HTO_seurat <- CreateSeuratObject(counts = hto,project = "HTO")
Adt_seurat <- CreateSeuratObject(counts = counts$`Antibody Capture`, project = "Anti")
rna_seurat <- CreateSeuratObject(counts = counts$`Gene Expression`, project = "RNA",min.cells = 3, min.features = 200)
rna_seurat
commonDrops <- Reduce("intersect",x=list(colnames(rna_seurat),colnames(HTO_seurat),colnames(Adt_seurat)))
length(commonDrops)
Adt_seurat 
head(rna_seurat)
Adt_seurat <- Adt_seurat[,commonDrops]
HTO_seurat <- HTO_seurat[,commonDrops]
rna_seurat <- rna_seurat[,commonDrops]
rna_seurat[["ADT"]] <- Adt_seurat
HTO_seurat[["RNA"]] <- CreateAssayObject(counts=rna_seurat[,commonDrops])
rna_seurat[["ADT"]] <- CreateAssayObject(counts = GetAssayData(Adt_seurat, slot = "counts"))
HTO_seurat[["RNA"]] <- CreateAssayObject(counts = GetAssayData(rna_seurat, slot = "counts"))
rna_seurat
head(rna_seurat)
rna_seurat[["ADT"]] <- CreateAssayObject(counts = Adt_seurat[,commonDrops])
HTO_seurat[["RNA"]] <- CreateAssayObject(counts=rna_seurat[,commonDrops])
Assays(rna_seurat)
```
 
```{r}
rna_seurat <- CreateSeuratObject(counts = counts$`Gene Expression`)

rna_seurat[["ADT"]] <- CreateAssayObject(counts = counts$`Antibody Capture`)
rna_seurat
head(rna_seurat)
DefaultAssay(rna_seurat) <- "ADT"
DefaultAssay(rna_seurat)
DefaultAssay(rna_seurat) <- "RNA"


```

```{r}
hto <- as.data.frame(counts$`Hashtag`)
rownames(hto)
hto <- hto[-c(1:5),]
rownames(hto)

commonDrops <- Reduce("intersect",x=list(colnames(rna_seurat),colnames(hto)))

length(commonDrops)

rna_seurat <- rna_seurat[,commonDrops]
hto <- hto[,commonDrops]

rna_seurat <- subset(rna_seurat, subset = nFeature_RNA > 200)


rna_seurat[["HTO"]] <- CreateAssayObject(counts = hto)
```

```{r}
rna_seurat <- NormalizeData(rna_seurat, 
                             assay = "HTO", 
                             normalization.method = "CLR")
```



```{r}
rna_seurat <- HTODemux(rna_seurat,
                        assay = "HTO", 
                        positive.quantile = 0.99)
```

```{r}
table(rna_seurat$HTO_classification.global)
```

```{r}
rna_seurat@assays
```

```{r}
table(rna_seurat$hash.ID)
```

```{r}
rna_seurat.subset <- subset(rna_seurat, 
                             idents = c("Negative","Doublet"), 
                             invert = TRUE)
table(Idents(rna_seurat.subset)) 

```

```{r}
IS_IEC_P6_03_15 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-6-Antibody"))
IS_IEC_P8_03_15 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-7-Antibody"))
IS_LP_P6_03_15 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-8-Antibody"))
IS_LP_P8_03_15 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-9-Antibody"))
CD4_03_15 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-10-Antibody"))
```

```{r}
table(rna_seurat$nCount_RNA)
```

```{r}
pbmc <- CreateSeuratObject(counts = counts, project = "pbmc3k", min.cells = 3, min.features = 200)
colnames(counts)
```


```{r}
data0323.dir <- "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0428/032323"
counts <- Read10X(data0323.dir)
hto <- as.data.frame(counts$`Hashtag`)
rownames(hto)
hto <- hto[-c(1:5),]
rownames(hto)
commonDrops <- Reduce("intersect",x=list(colnames(rna_seurat),colnames(hto)))
length(commonDrops)

rna_seurat <- rna_seurat[,commonDrops]
hto <- hto[,commonDrops]

rna_seurat <- subset(rna_seurat, subset = nFeature_RNA > 200)


rna_seurat[["HTO"]] <- CreateAssayObject(counts = hto)


```

```{r}
data0323.dir <- "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0428/032323"
counts <- Read10X(data0323.dir)
hto <- as.data.frame(counts$`Hashtag`)
rownames(hto)
hto <- hto[-c(1:5),]
rownames(hto)
```


```{r}
seurat <- CreateSeuratObject(counts = counts$`Gene Expression`)
seurat[["ADT"]] <- CreateAssayObject(counts = counts$`Antibody Capture`)
seurat
head(seurat)

```

```{r}
commonDrops <- Reduce("intersect",x=list(colnames(seurat),colnames(hto)))
length(commonDrops)
seurat <- subset(seurat, subset = nFeature_RNA > 100)
seurat <- seurat[,commonDrops]
hto <- hto[,commonDrops]

```

```{r}
# Normalize RNA data with log normalization
pbmc.hashtag <- NormalizeData(seurat)
# Find and scale variable features
pbmc.hashtag <- FindVariableFeatures(pbmc.hashtag, selection.method = "mean.var.plot")
pbmc.hashtag <- ScaleData(pbmc.hashtag, features = VariableFeatures(pbmc.hashtag))
```
```{r}
pbmc.hashtag[["HTO"]] <- CreateAssayObject(counts = hto)
```

```{r}
rna_seurat <- NormalizeData(pbmc.hashtag , 
                             assay = "HTO", 
                             normalization.method = "CLR")
```

```{r}
rna_seurat <- HTODemux(rna_seurat,
                        assay = "HTO", 
                        positive.quantile = 0.99)
```


```{r}
seurat[["HTO"]] <- CreateAssayObject(counts = hto)

```

```{r}
data0323.dir <- "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0428/032323"
counts <- Read10X(data0323.dir)
hto <- as.data.frame(counts$`Hashtag`)
rownames(hto)
hto <- hto[-c(1:5),]
rownames(hto)

rna_seurat <- CreateSeuratObject(counts = counts$`Gene Expression`)
rna_seurat[["ADT"]] <- CreateAssayObject(counts = counts$`Antibody Capture`)
rna_seurat
head(rna_seurat)


rna_seurat <- subset(rna_seurat, subset = nFeature_RNA > 200)
commonDrops <- Reduce("intersect",x=list(colnames(rna_seurat),colnames(hto)))
length(commonDrops)
rna_seurat <- rna_seurat[,commonDrops]
hto <- hto[,commonDrops]

rna_seurat [["HTO"]] <- CreateAssayObject(counts = hto)

rna_seurat <- NormalizeData(rna_seurat , 
                             assay = "HTO", 
                             normalization.method = "CLR")

rna_seurat <- HTODemux(rna_seurat,
                        assay = "HTO", 
                        positive.quantile = 0.99)

table(rna_seurat$HTO_classification.global)

rna_seurat@assays

table(rna_seurat$hash.ID)

P1 <- RidgePlot(object = rna_seurat, features = rownames(GetAssayData(pbmc.hashtag, assay = "HTO"))[1:5])

ggsave(filename = "gene expression0323.png", plot = P1, width = 20, height = 15,dpi = 300)

P1

Idents(rna_seurat) <- "HTO_classification.global"
p2 <- VlnPlot(rna_seurat, features = "nCount_RNA", pt.size = 0.1, log = TRUE)
ggsave(filename = "gene expression0323_single.png", plot = p2,dpi = 300)
p2

rna_seurat.subset <- subset(rna_seurat, 
                             idents = c("Negative","Doublet"), 
                             invert = TRUE)

table(Idents(rna_seurat.
             subset))
table(rna_seurat.subset$hash.ID)

Idents(rna_seurat.subset) <- "hash.ID"

IS_IEC_P6_03_15 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-6-Antibody"))
IS_IEC_P8_03_15 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-7-Antibody"))
IS_LP_P6_03_15 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-8-Antibody"))
IS_LP_P8_03_15 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-9-Antibody"))
CD4_03_15 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-10-Antibody"))
```

```{r}
BiocManager::install("MULTIseqDemux")
library(MULTIseqDemux)
```
```{r}
rna_seurat <- MULTIseqDemux(rna_seurat, assay = "HTO", known = NULL, method = "kmeans", dims = 1:10, cells.use = NULL, resolution = 0.5)
```



```{r}
data_dirs <- c("/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0619/51023",             
               "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0619/51723")
for (dir in data_dirs) {
  # read data
  counts <- Read10X(dir)
  
  # rest of your processing steps...
  hto <- as.data.frame(counts$`Hashtag`)
  rownames(hto)
hto <- hto[-c(1:5),]
rownames(hto)

rna_seurat <- CreateSeuratObject(counts = counts$`Gene Expression`)
rna_seurat[["ADT"]] <- CreateAssayObject(counts = counts$`Antibody Capture`)
rna_seurat
head(rna_seurat)


rna_seurat <- subset(rna_seurat, subset = nFeature_RNA > 300)
commonDrops <- Reduce("intersect",x=list(colnames(rna_seurat),colnames(hto)))
length(commonDrops)
rna_seurat <- rna_seurat[,commonDrops]
hto <- hto[,commonDrops]

rna_seurat [["HTO"]] <- CreateAssayObject(counts = hto)

rna_seurat <- NormalizeData(rna_seurat , 
                             assay = "HTO", 
                             normalization.method = "CLR")

rna_seurat <- HTODemux(rna_seurat,
                        assay = "HTO", 
                        positive.quantile = 0.99)

table(rna_seurat$HTO_classification.global)

rna_seurat@assays

table(rna_seurat$hash.ID)

  # create RidgePlot and VlnPlot
  P1 <- RidgePlot(object = rna_seurat, features = rownames(GetAssayData(rna_seurat, assay = "HTO"))[1:5])
  Idents(rna_seurat) <- "HTO_classification.global"
  p2 <- VlnPlot(rna_seurat, features = "nCount_RNA", pt.size = 0.1, log = TRUE)

  # generate a unique name for each plot
  dir_name <- gsub("/", "_", dir)
  ridgeplot_name <- paste0("RidgePlot_", dir_name, ".png")
  vlnplot_name <- paste0("VlnPlot_", dir_name, ".png")

  # save plots to disk
  ggsave(filename = ridgeplot_name, plot = P1, width = 20, height = 15, dpi = 300)
  ggsave(filename = vlnplot_name, plot = p2, dpi = 300)
  
  # subset Seurat objects for each unique hash.ID
  hash_IDs <- unique(Idents(rna_seurat.subset))
  for (hash_ID in hash_IDs) {
    subset_obj <- subset(rna_seurat.subset, idents = c(hash_ID))
    
    # generate a unique name for each subset
    subset_name <- paste0(dir_name, "_", hash_ID, ".rds")
    
    # save subset to disk
    saveRDS(subset_obj, file = subset_name)
  }
}
```

```{r}
IS_IEC_P6_03_15 <- readRDS("_Users_chaotingzhou_Documents_Cadwell-lab_Single_Cells_HR_0428_032323_anti-human-Hashtag-6-Antibody.rds")
```

```{r}
data_dirs <- c(
                    
               
            
              
               "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0113/12-20-22"
               )
for (dir in data_dirs) {
  # read data
  counts <- Read10X(dir)
  
  # rest of your processing steps...
  hto <- as.data.frame(counts$`Hashtag`)
  rownames(hto)
hto <- hto[-c(1:5),]
rownames(hto)

rna_seurat <- CreateSeuratObject(counts = counts$`Gene Expression`)
rna_seurat[["ADT"]] <- CreateAssayObject(counts = counts$`Antibody Capture`)
rna_seurat
head(rna_seurat)


rna_seurat <- subset(rna_seurat, subset = nFeature_RNA > 200)
commonDrops <- Reduce("intersect",x=list(colnames(rna_seurat),colnames(hto)))
length(commonDrops)
rna_seurat <- rna_seurat[,commonDrops]
hto <- hto[,commonDrops]

rna_seurat [["HTO"]] <- CreateAssayObject(counts = hto)

rna_seurat <- NormalizeData(rna_seurat , 
                             assay = "HTO", 
                             normalization.method = "CLR")

rna_seurat <- HTODemux(rna_seurat,
                        assay = "HTO", 
                        positive.quantile = 0.99)

table(rna_seurat$HTO_classification.global)

rna_seurat@assays

table(rna_seurat$hash.ID)

  # create RidgePlot and VlnPlot
  P1 <- RidgePlot(object = rna_seurat, features = rownames(GetAssayData(rna_seurat, assay = "HTO"))[1:5])
  Idents(rna_seurat) <- "HTO_classification.global"
  p2 <- VlnPlot(rna_seurat, features = "nCount_RNA", pt.size = 0.1, log = TRUE)

  # generate a unique name for each plot
  dir_name <- gsub("/", "_", dir)
  ridgeplot_name <- paste0("RidgePlot_", dir_name, ".png")
  vlnplot_name <- paste0("VlnPlot_", dir_name, ".png")

  # save plots to disk
  ggsave(filename = ridgeplot_name, plot = P1, width = 20, height = 15, dpi = 300)
  ggsave(filename = vlnplot_name, plot = p2, dpi = 300)
  
  rna_seurat.subset <- subset(rna_seurat, 
                             idents = c("Negative","Doublet"), 
                             invert = TRUE)
  table(Idents(rna_seurat.subset))
  table(rna_seurat.subset$hash.ID)
  Idents(rna_seurat.subset) <- "hash.ID"
  
  # subset Seurat objects for each unique hash.ID
  hash_IDs <- unique(Idents(rna_seurat.subset))
  for (hash_ID in hash_IDs) {
    subset_obj <- subset(rna_seurat.subset, idents = c(hash_ID))
    
    # generate a unique name for each subset
    subset_name <- paste0(dir_name, "_", hash_ID, ".rds")
    
    # save subset to disk
    saveRDS(subset_obj, file = subset_name)
  }
}
```

```{r}
data0323.dir <- "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0428/patient_12_13"
counts <- Read10X(data0323.dir)
hto <- as.data.frame(counts$`Hashtag`)
rownames(hto)
hto <- hto[-c(1:5),]
rownames(hto)

rna_seurat <- CreateSeuratObject(counts = counts$`Gene Expression`)
rna_seurat[["ADT"]] <- CreateAssayObject(counts = counts$`Antibody Capture`)
rna_seurat
head(rna_seurat)


rna_seurat <- subset(rna_seurat, subset = nFeature_RNA > 200)
commonDrops <- Reduce("intersect",x=list(colnames(rna_seurat),colnames(hto)))
length(commonDrops)
rna_seurat <- rna_seurat[,commonDrops]
hto <- hto[,commonDrops]

rna_seurat [["HTO"]] <- CreateAssayObject(counts = hto)

rna_seurat <- NormalizeData(rna_seurat , 
                             assay = "HTO", 
                             normalization.method = "CLR")

rna_seurat <- HTODemux(rna_seurat,
                        assay = "HTO", 
                        positive.quantile = 0.99)

table(rna_seurat$HTO_classification.global)

rna_seurat@assays

table(rna_seurat$hash.ID)

P1 <- RidgePlot(object = rna_seurat, features = rownames(GetAssayData(pbmc.hashtag, assay = "HTO"))[1:5])

ggsave(filename = "gene expression0323.png", plot = P1, width = 20, height = 15,dpi = 300)

P1

Idents(rna_seurat) <- "HTO_classification.global"
p2 <- VlnPlot(rna_seurat, features = "nCount_RNA", pt.size = 0.1, log = TRUE)
ggsave(filename = "gene expression0323_single.png", plot = p2,dpi = 300)
p2

rna_seurat.subset <- subset(rna_seurat, 
                             idents = c("Negative","Doublet"), 
                             invert = TRUE)

table(Idents(rna_seurat.
             subset))
table(rna_seurat.subset$hash.ID)

Idents(rna_seurat.subset) <- "hash.ID"


```


```{r}
IS_IEC_P6_03_15 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-6-Antibody"))
IS_IEC_P8_03_15 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-7-Antibody"))
IS_LP_P6_03_15 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-8-Antibody"))
IS_LP_P8_03_15 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-9-Antibody"))
CD4_03_15 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-10-Antibody"))
```


```{r}
data_dirs <- c( "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0113/12-01-22")
for (dir in data_dirs) {
  # read data
  counts <- Read10X(dir)
  
  # rest of your processing steps...
  hto <- as.data.frame(counts$`Hashtag`)
  rownames(hto)
hto <- hto[-c(1:5),]
rownames(hto)

rna_seurat <- CreateSeuratObject(counts = counts$`Gene Expression`)
rna_seurat[["ADT"]] <- CreateAssayObject(counts = counts$`Antibody Capture`)
rna_seurat
head(rna_seurat)


rna_seurat <- subset(rna_seurat, subset = nFeature_RNA > 200)
commonDrops <- Reduce("intersect",x=list(colnames(rna_seurat),colnames(hto)))
length(commonDrops)
rna_seurat <- rna_seurat[,commonDrops]
hto <- hto[,commonDrops]

rna_seurat [["HTO"]] <- CreateAssayObject(counts = hto)

rna_seurat <- NormalizeData(rna_seurat , 
                             assay = "HTO", 
                             normalization.method = "CLR")

rna_seurat <- HTODemux(rna_seurat,
                        assay = "HTO", 
                        positive.quantile = 0.99)

table(rna_seurat$HTO_classification.global)

rna_seurat@assays

table(rna_seurat$hash.ID)

  # create RidgePlot and VlnPlot
  P1 <- RidgePlot(object = rna_seurat, features = rownames(GetAssayData(rna_seurat, assay = "HTO"))[1:5])
  Idents(rna_seurat) <- "HTO_classification.global"
  p2 <- VlnPlot(rna_seurat, features = "nCount_RNA", pt.size = 0.1, log = TRUE)

  # generate a unique name for each plot
  dir_name <- gsub("/", "_", dir)
  ridgeplot_name <- paste0("RidgePlot_", dir_name, ".png")
  vlnplot_name <- paste0("VlnPlot_", dir_name, ".png")

  # save plots to disk
  ggsave(filename = ridgeplot_name, plot = P1, width = 20, height = 15, dpi = 300)
  ggsave(filename = vlnplot_name, plot = p2, dpi = 300)
  
  rna_seurat.subset <- subset(rna_seurat, 
                             idents = c("Negative","Doublet"), 
                             invert = TRUE)
  table(Idents(rna_seurat.subset))
  table(rna_seurat.subset$hash.ID)
  Idents(rna_seurat.subset) <- "hash.ID"
  
  # subset Seurat objects for each unique hash.ID
  hash_IDs <- unique(Idents(rna_seurat.subset))
  for (hash_ID in hash_IDs) {
    subset_obj <- subset(rna_seurat.subset, idents = c(hash_ID))
    
    # generate a unique name for each subset
    subset_name <- paste0(dir_name, "_", hash_ID, ".rds")
    
    # save subset to disk
    saveRDS(subset_obj, file = subset_name)
  }
}


```
```{r}
library(Matrix)

# Define file paths
matrix_file <- "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0113/12-01-22/matrix.mtx"
barcodes_file <- "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0407/0315/barcodes.tsv.gz"
features_file <- "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0113/12-01-22/features.tsv"
```

```{r}
matrix <- readMM(file = matrix_file)
barcodes <- read.table(barcodes_file)
features <- read.table(features_file)
```


```{r}
dim(matrix)
dim(barcodes)
dim(features)
```

```{r}
pbmc.counts <- Read10X(data.dir = "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0113/12-01-22")
```

```{r}
counts <- Read10X(data.dir = "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0113/12-01-22")
  
  # rest of your processing steps...
  hto <- as.data.frame(counts$`Antibody Capture`)
  rownames(hto)

rna_seurat <- CreateSeuratObject(counts = counts$`Gene Expression`)
rna_seurat[["ADT"]] <- CreateAssayObject(counts = counts$`Antibody Capture`)
rna_seurat
head(rna_seurat)


rna_seurat <- subset(rna_seurat, subset = nFeature_RNA > 200)
commonDrops <- Reduce("intersect",x=list(colnames(rna_seurat),colnames(hto)))
length(commonDrops)
rna_seurat <- rna_seurat[,commonDrops]
hto <- hto[,commonDrops]

rna_seurat [["HTO"]] <- CreateAssayObject(counts = hto)

rna_seurat <- NormalizeData(rna_seurat , 
                             assay = "HTO", 
                             normalization.method = "CLR")

rna_seurat <- HTODemux(rna_seurat,
                        assay = "HTO", 
                        positive.quantile = 0.99)

table(rna_seurat$HTO_classification.global)

rna_seurat@assays

table(rna_seurat$hash.ID)
```

```{r}
  P1 <- RidgePlot(object = rna_seurat, features = rownames(GetAssayData(rna_seurat, assay = "HTO"))[1:5])
  Idents(rna_seurat) <- "HTO_classification.global"
  p2 <- VlnPlot(rna_seurat, features = "nCount_RNA", pt.size = 0.1, log = TRUE)

  # save plots to disk
  ggsave(filename = "1201.png", plot = P1, width = 20, height = 15, dpi = 300)
  ggsave(filename = "vlnplot_1201.png", plot = p2, dpi = 300)
```

```{r}
rna_seurat.subset <- subset(rna_seurat, 
                             idents = c("Negative","Doublet"), 
                             invert = TRUE)
  table(Idents(rna_seurat.subset))
  table(rna_seurat.subset$hash.ID)
  Idents(rna_seurat.subset) <- "hash.ID"
```

```{r}
subset_obj <- subset(rna_seurat.subset, idents = c(hash_ID))
    
    # generate a unique name for each subset
    subset_name <- paste0(dir_name, "_", hash_ID, ".rds")
    
    # save subset to disk
    saveRDS(subset_obj, file = subset_name)
```


```{r}
IS_IEC_P6_12_01_IEC_P15 <- subset(rna_seurat.subset ,
               idents = c("HT6"))
IS_IEC_P7_12_01_LP_P15 <- subset(rna_seurat.subset ,
               idents = c("HT7"))
IS_LP_P8__12_01_IEC_P19 <- subset(rna_seurat.subset ,
               idents = c("HT8"))
IS_LP_P9__12_01_LP_P19 <- subset(rna_seurat.subset ,
               idents = c("HT9"))
CD4__12_01 <- subset(rna_seurat.subset ,
               idents = c("HT10"))
```

```{r}
saveRDS(IS_IEC_P6_12_01_IEC_P15, file = "IS_IEC_P6_12_01_IEC_P15.rds")
saveRDS(IS_IEC_P7_12_01_LP_P15, file = "IS_IEC_P7_12_01_LP_P15.rds")
saveRDS(IS_LP_P8__12_01_IEC_P19, file = "IS_LP_P8__12_01_IEC_P19.rds")
saveRDS(IS_LP_P9__12_01_LP_P19, file = "IS_LP_P9__12_01_LP_P19.rds")
saveRDS(CD4__12_01, file = "CD4__12_01.rds")
```


```{r}
data0323.dir <- "/Users/chaotingzhou/Documents/Cadwell-lab/Single_Cells_HR/0619/51723"
counts <- Read10X(data0323.dir)
hto <- as.data.frame(counts$`Hashtag`)
rownames(hto)
hto <- hto[-c(1:6),]
rownames(hto)

rna_seurat <- CreateSeuratObject(counts = counts$`Gene Expression`)
rna_seurat[["ADT"]] <- CreateAssayObject(counts = counts$`Antibody Capture`)
rna_seurat
head(rna_seurat)


rna_seurat <- subset(rna_seurat, subset = nFeature_RNA > 200)
commonDrops <- Reduce("intersect",x=list(colnames(rna_seurat),colnames(hto)))
length(commonDrops)
rna_seurat <- rna_seurat[,commonDrops]
hto <- hto[,commonDrops]

rna_seurat [["HTO"]] <- CreateAssayObject(counts = hto)

rna_seurat <- NormalizeData(rna_seurat , 
                             assay = "HTO", 
                             normalization.method = "CLR")

rna_seurat_1 <- MULTIseqDemux(object = rna_seurat, assay = "HTO")

rna_seurat_D <- HTODemux(rna_seurat,
                        assay = "HTO", 
                        positive.quantile = 0.99)

table(rna_seurat_D$HTO_classification.global)

rna_seurat@assays

table(rna_seurat_D$hash.ID)

P1 <- RidgePlot(object = rna_seurat_D, features = rownames(GetAssayData(rna_seurat_D, assay = "HTO"))[1:5])
P1

ggsave(filename = "MAY17.png", plot = P1, width = 20, height = 15,dpi = 300)

P1

Idents( rna_seurat_D) <- "HTO_classification.global"
p2 <- VlnPlot(rna_seurat_D, features = "nCount_RNA", pt.size = 0.1, log = TRUE)
p2
ggsave(filename = "MAY17_single.png", plot = p2,dpi = 300)
p2

rna_seurat.subset <- subset(rna_seurat_D, 
                             idents = c("Negative","Doublet"), 
                             invert = TRUE)

table(Idents(rna_seurat.
             subset))
table(rna_seurat.subset$hash.ID)

Idents(rna_seurat.subset) <- "hash.ID"
```

```{r}
P1 <- RidgePlot(object = rna_seurat, features = rownames(GetAssayData(rna_seurat, assay = "HTO"))[1:5])
  Idents(rna_seurat) <- "HTO_classification.global"
  p2 <- VlnPlot(rna_seurat, features = "nCount_RNA", pt.size = 0.1, log = TRUE)

  # save plots to disk
  ggsave(filename = "1220.png", plot = P1, width = 20, height = 15, dpi = 300)
  ggsave(filename = "vlnplot_1220.png", plot = p2, dpi = 300)
```

```{r}
rna_seurat.subset <- subset(rna_seurat, 
                             idents = c("Negative","Doublet"), 
                             invert = TRUE)
  table(Idents(rna_seurat.subset))
  table(rna_seurat.subset$hash.ID)
  Idents(rna_seurat.subset) <- "hash.ID"
```

```{r}
IEC_HT6_12_20_IEC_P3 <- subset(rna_seurat.subset ,
               idents = c("HT6"))
IEC_HT7_12_20_LP_P4 <- subset(rna_seurat.subset ,
               idents = c("HT7"))
LP_HT8__12_20_IEC_P3 <- subset(rna_seurat.subset ,
               idents = c("HT8"))
LP_HT9__12_20_LP_P4 <- subset(rna_seurat.subset ,
               idents = c("HT9"))
CD4__12_20 <- subset(rna_seurat.subset ,
               idents = c("HT10"))
```


```{r}
IEC_HT7_05_17_IEC_P5 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-7-Antibody"))
IEC_HT8_05_17_LP_P5 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-8-Antibody"))
LP_HT9_05_17_LP19_all <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-9-Antibody"))
LP_HT9__12_20_LP_P4 <- subset(rna_seurat.subset ,
               idents = c("HT9"))
CD4__MAY_17 <- subset(rna_seurat.subset ,
               idents = c("anti-human-Hashtag-10-Antibody"))
```



```{r}
saveRDS(IEC_HT7_05_17_IEC_P5, file = "IEC_HT7_05_17_IEC_P5.rds")
saveRDS(IEC_HT8_05_17_LP_P5, file = "IEC_HT8_05_17_LP_P5 .rds")
saveRDS(LP_HT9_05_17_LP19_all, file = "LP_HT9_05_17_LP19_all.rds")
saveRDS(CD4__MAY_17 , file = "CD4__MAY_17.rds")
saveRDS(CD4__12_20, file = "CD4__12_20.rds")
```


```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
